---
title: "Group Project"
author: "Group3(Xinyi Yang, Tong Niu, Yvonne Hao)"
date: "4/27/2020"
output:
  word_document: yes
  pdf_document: yes
  html_document: yes
---

#Set Up
upload package
```{r}
rm(list = ls())
library(readr)
library(tidyverse)
library(ggplot2)
library(corrplot)

```

#Load Data
```{r}
attrition <- read_csv("WA_Fn-UseC_-HR-Employee-Attrition.csv", 
    col_types = cols(Education = col_character(), 
        EnvironmentSatisfaction = col_character(), 
        JobInvolvement = col_character(), 
        JobLevel = col_character(), JobSatisfaction = col_character(), 
        PerformanceRating = col_character(), 
        RelationshipSatisfaction = col_character(), 
        StockOptionLevel = col_character(), 
        WorkLifeBalance = col_character()))
View(attrition)
```
#Data Preparation
#check the missing value
```{r}
sum(is.na(attrition))
```


#Statistic Summary
```{r}
glimpse(attrition)
```

```{r}
summary(attrition)
```


```{r}
attrition <- attrition%>%
  mutate(
    Attrition=as.factor(Attrition),
    BusinessTravel=as.factor(BusinessTravel),
    Department=as.factor(Department),
    Education=as.factor(Education),
    EducationField=as.factor(EducationField),
    EnvironmentSatisfaction=as.factor(EnvironmentSatisfaction),
    Gender=as.factor(Gender),
    JobInvolvement=as.factor(JobInvolvement),
    JobLevel=as.factor(JobLevel),
    JobRole=as.factor(JobRole),
    JobSatisfaction=as.factor(JobSatisfaction),
    MaritalStatus=as.factor(MaritalStatus),
    Over18=as.factor(Over18),
    OverTime=as.factor(OverTime),
    PerformanceRating=as.factor(PerformanceRating),
    RelationshipSatisfaction=as.factor(RelationshipSatisfaction),
    StockOptionLevel=as.factor(StockOptionLevel),
    WorkLifeBalance=as.factor(WorkLifeBalance))

summary(attrition)
```


#Data Visualization

##Categoric factors

Using Bar Chart to find the distribution relationship of categoric factors

```{r}
attrition %>%
  ggplot(aes(x=BusinessTravel,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=Department,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=Education,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=EducationField,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=EnvironmentSatisfaction,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=Gender,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=JobInvolvement,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=JobLevel,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=JobRole,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=JobSatisfaction,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=MaritalStatus,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=Over18,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=OverTime,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=PerformanceRating,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=RelationshipSatisfaction,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=StockOptionLevel,fill=Attrition)) +
  geom_bar()

attrition %>%
  ggplot(aes(x=WorkLifeBalance,fill=Attrition)) +
  geom_bar()

```

##Numeric factors
### Histogram Chart
Using Histogram Chart to find the distribution relationship of MonthlyIncome and MonthlyRate
```{r}

attrition %>%
  ggplot(aes(x=MonthlyIncome,fill=Attrition)) +
  geom_histogram(binwidth=500,alpha=.5,position="identity")

attrition %>%
  ggplot(aes(x=MonthlyRate,fill=Attrition)) +
  geom_histogram(binwidth=500,alpha=.5,position="identity")


```
### Box Plot
Using Box Plot to find the distribution relationship of other numeric factors
```{r}
ggplot(attrition,aes(x=Attrition,y=Age,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=DailyRate,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=DistanceFromHome,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=EmployeeCount,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=EmployeeNumber,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=HourlyRate,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=NumCompaniesWorked,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=PercentSalaryHike,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=StandardHours,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=TotalWorkingYears,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=TrainingTimesLastYear,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=YearsAtCompany,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=YearsInCurrentRole,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=YearsSinceLastPromotion,fill=Attrition))+geom_boxplot()

ggplot(attrition,aes(x=Attrition,y=YearsWithCurrManager,fill=Attrition))+geom_boxplot()

```
From the boxplot we could find that there are two unmeaningful factors:employeeCount and StandardHours. And they will not be the variables in further classification model.



##HeatMap

Using heatmap we could find the relationship between numeric variables

```{r}
numeric_attrition <- attrition[,c(1,4,6,10,13,19,20,21,24,29,30,32:35)]
numeric_Attrition = as.numeric(attrition$Attrition)- 1
numeric_attrition = cbind(numeric_attrition, numeric_Attrition)
str(numeric_attrition)

M <- cor(numeric_attrition)
corrplot(M, method="circle")
```



#Classification
```{r}

```

